### 2013-02-15 doc/icml2013/evaluation.tex

\subsection{Setup}

@@

We ran expectation-maximization until the log likelihood converged
$10^-5$. Initialized the entries of $\beta$ with a random Gaussian, $\normal{0}{1}$.

In all our experiments, EM converged.

Describe spectral (briefly pointing to algorithm);
initialization, clipping.

Describe spectral+EM

\paragraph{Datasets}
Describe the Curves dataset.
$x = (1, t, t^4, t^9)$
$d = b^p$

>>>>

\subsection{Experimental Setup}

@@

We implemented the Spectral Experts algorithm using a proximal
subgradient descent algorithm\citationneeded for the low rank recovery
of $M_2$ and $M_3$. The algorithm was initialized with the regularized
least squares solution and was run to convergence in each instance. Both
regularization parameters were annealed as $\frac{1}{\sqrt{T}}$.

We also implemented EM for this problem. In one set of experiments, we
initialized the parameters $\beta$ with random Gaussian entries with
mean zero and variance 1 and the mixture probabilities $\pi$ were
initialized to be uniform. We also compared the performance of EM when
initialized with the starting points given by Spectral Experts. We ran
EM for at most 1000 iterations, but in practice the experiments always
converged before this.

\paragraph{Datasets}

We ran our experiments on synthetically generated non-linear data. To
conform to the identifiability criteria discussed in
\sectionref{sec:algo}, we considered only features that would guarantee
this condition.

\begin{figure*}[t]
  \centering
  \subfigure{}{
    \includegraphics[width=0.30\textwidth]{figures/curves-vis/1-8-3-spec.png}}
  \subfigure{}{
    \includegraphics[width=0.30\textwidth]{figures/curves-vis/1-8-3-em.png}}
  \subfigure{}{
    \includegraphics[width=0.30\textwidth]{figures/curves-vis/1-8-3-spem.png}}
  \label{fig:curves}
\end{figure*}

As an example, in the one dimensional scenario, one set of features we
considered were $\{1, x, x^4, x^7\}$. The data and the curves fit using
the spectral algorithm, EM with random initializations and EM
initialized with the parameters recovered using spectral experts are
plotted in \figureref{fig:curves}.

We generated $x$ uniformly from the unit hypercube.

Describe the Curves dataset.
$x = (1, t, t^4, t^9)$
$d = b^p$
